---
title: Site locations
format: html
editor: source

execute:
  eval: true
  warning: false
  message: false
  echo: false
---

```{r}
library(tidyverse)
library(here)
library(leaflet)
library(crosstalk) # use v1.1.1 to remove (All) from table filter selection
library(DT)
library(shiny)

data(tfwdat)
data(locs)
```

*Site last updated `r Sys.Date()`*

The map shows all of the locations with a litter collection device.  Select a site from the table to view the location on the map.  The total events indicates the number of dates when litter and debris were collected and enumerated at a site.  The total lbs shows the total weight of all items collected for all events at a site.  

All litter and debris were sampled using the [ETAP method](https://www.epa.gov/system/files/documents/2021-09/revised_final_etap_june2021.pdf){target="_blank"}. Litter includes items that can be assigned to an ETAP category and debris includes items without a category (usually large, specific items).  For each site and date, only a subset of litter and debris is categorized if the total amount collected exceeds two bags. ETAP provides an overview of the ratios of each type of material found at a site, whereas the total weight is the weight of all the litter and debris found in the device at the collection date.

```{r}
# summarize events by site
sitsum <- tfwdat %>% 
  group_by(Site) %>% 
  summarise(
    nevnt = length(unique(Date)), 
    totlbs = sum(LitterRecyclablesWeightLb, LitterTrashWeightLb, DebrisRecyclablesWeightLb, DebrisTrashWeightLb, na.rm = T)
  )

# locations combined with all site data
tomap <- locs %>% 
  select(Site, County, lon, lat) %>% 
  unique %>% 
  left_join(sitsum, by = 'Site') %>% 
  mutate(
    nevnt = ifelse(is.na(nevnt), 0, nevnt), 
    totlbs = round(totlbs, 1),
    lab = paste0("<b>Site</b>: ", Site, '<br/><b>County</b>: ', County, '<br/><b>Number of events</b>: ', nevnt, '<br/><b>Total (lbs)</b>: ', totlbs),
    lab = lapply(lab, HTML)
  ) %>% 
  select(Site, County, `Number of events` = nevnt, `Total (lbs)` = totlbs, lab, lon, lat)

sd <- SharedData$new(tomap)

leaflet(sd) %>% 
  addProviderTiles(providers$CartoDB.Positron) %>% 
  addMarkers(lng = ~lon, lat = ~lat, label = ~lab)
datatable(sd, extensions="Scroller", style="bootstrap", class="compact", width="100%", rownames = F,
          options=list(deferRender=TRUE, scrollY=300, scroller=F, dom = 'ltp',
                       columnDefs = list(
                         list(visible=FALSE, targets=c(4, 5, 6)),
                         list(className = 'dt-left', targets = '_all')
                         )
          ))
```