---
title: Site tabular data
format: html
editor: source

execute:
  eval: true
  warning: false
  message: false
  echo: false
---

```{r}
library(tidyverse)
library(crosstalk) # use v1.1.1 to remove (All) from table filter selection
library(DT)

data(tfwdat)
```

These tables show the litter and debris collected at a site for a given date.  The first table shows counts by category using the [ETAP method](https://www.epa.gov/system/files/documents/2021-09/revised_final_etap_june2021.pdf){target="_blank"} and the second table shows the total pounds by category.  Note that counts in the first table are from a subset of the total bags collected at a site and date if more than two bags were collected, whereas the total weights in the second table include all the litter and debris collected.

```{r}
tab1 <- tfwdat %>%
  unite('sitedate', Site, Date, sep = ' - ') %>%   
  select(sitedate, dataCards) %>% 
  unnest('dataCards') %>% 
  arrange(sitedate, -itemcnt) %>%
  select(item1, item2, itemcnt, sitedate)
tab2 <- tfwdat %>% 
  unite('sitedate', Site, Date, sep = ' - ') %>% 
  select(LitterTrashWeightLb, LitterRecyclablesWeightLb, DebrisTrashWeightLb, DebrisRecyclablesWeightLb, sitedate)
totab1 <- SharedData$new(tab1, ~sitedate, group = 'choose site date')
totab2 <- SharedData$new(tab2, ~sitedate, group = 'choose site date')

filter_select(id = "filter1", label = "Select site and date", sharedData = totab1, group = ~sitedate, multiple = F)#,
datatable(totab1, extensions = "Scroller", style = "bootstrap", class = "compact", width="100%", rownames = F, caption = 'Items found', 
            options=list(scrollY=400, scroller=TRUE,
                         columnDefs = list(
                           list(visible = F, targets = 3),
                           list(className = 'dt-left', targets = '_all')
                           )
                         ), 
            colnames = c('Item 1', 'Item 2', 'Count', 'sitedate'))
datatable(totab2, extensions = "Scroller", style = "bootstrap", class = "compact", width="100%", rownames = F, caption = 'Total pounds by category',
          options=list(scrollY=300, scroller=TRUE, dom = 'ltp',
                       columnDefs = list(
                         list(visible = F, targets = 4),
                         list(className = 'dt-left', targets = '_all')
                         )
                       ),
          colnames = c('Litter Trash', 'Litter Recyclables', 'Debris trash', 'Debris Recyclables', 'sitedate')
  )
```

```{js}
function filter_default() {
    document.getElementById("filter1").getElementsByClassName("selectized")[0].selectize.setValue("HC_SB_Cotanchobee - 2021-06-29", false);
}
window.onload = filter_default;
```

<!-- <script type="text/javascript" src="js/iframeResizer.contentWindow.min.js"></script> -->
